A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-11 article/02_Materials_and_Methods.Rmd
improvements of table

To test for correlation between the distances based on the variables *burial type* and *burial construction*, the time frame of interest was divided into sections of 200 years. For each section of each the two variables, a matrix of the mean SED over time was calculated. The two matrices of each section can be tested for correlation with the Mantel test, which uses permutations of allegedly correlating matrices to determine how strongly random reordering can alter an underlying correlation coefficient [@mantelDetectionDiseaseClustering1967]. Since both distances compared here, *burial type* and *burial construction* distance, are cardinal scale variables, the Pearson correlation coefficient [@pearsonNotesRegressionInheritance1895] can be applied as a base measure for the Mantel test. The mean correlation for each of the $\frac{8*8}{2}-\frac{8}{2}=28$ region-region relations can be plotted in the *burial type*SED-*burial construction*SED space (Figure **TODO**).

>>>>

To test for correlation between the distances based on the variables *burial type* and *burial construction*, the time frame of interest was divided into sections of 200 years. For each section of each the two variables, a matrix of the mean SED over time was calculated. The two matrices of each section can be tested for correlation with the Mantel test, which uses permutations of allegedly correlating matrices to determine how strongly random reordering can alter an underlying correlation coefficient [@mantelDetectionDiseaseClustering1967]. Since both distances compared here, *burial type* and *burial construction* distance, are cardinal scale variables, the Pearson correlation coefficient [@pearsonNotesRegressionInheritance1895] can be applied as a base measure for the Mantel test. The test result are listed in Table \ref{distance_and_correlation_table}.

```{r, echo = FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
knitr::kable(
  distance_and_correlation_table, 
  "latex", 
  caption = "\\label{distance_and_correlation_table}Demo table", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace"
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type" = 3, "burial construction" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```
